### 2022-05-27 chapters/04-chapter-4.tex
txs auto checkin

%		\begin{longtable}[l]{  @{}| p{0.7cm} | p{5cm} | p{2cm} | p{2cm} | p{4cm} | @{} }
%			\caption{Kasus-kasus pengujian}
%			\label{testcase-i}                                                           
%			\\ \hline
%			\centering\bfseries{ID} & \centering\bfseries{Service (Fungsi)} & \centering\bfseries{Extra Latency} & \centering\bfseries{User} & \centering\bfseries{Keterangan} \tabularnewline \hline
%			\endfirsthead
%			I1 & CheckoutService (placeorder) &  \centering{100ms} & \centering{25} & Kasus extra latency \#1 \\ \hline
%				
%		\end{longtable}
\begin{table}[]
	\begin{tabular}{lllll}
		\cline{1-4}
		\multicolumn{1}{|c|}{ID} & \multicolumn{1}{c|}{Service (Fungsi)} & \multicolumn{1}{l|}{Extra Latency} & \multicolumn{1}{l|}{User} & Keterangan              \\ \cline{1-4}
		I1                       & CheckoutService (placeorder)          & 100ms                              & 25                        & Kasus extra latency \#1
	\end{tabular}
\end{table}

>>>>

%		\begin{longtable}[l]{  @{}| p{0.7cm} | p{5cm} | p{2cm} | p{2cm} | p{4cm} | @{} }
%			\caption{Kasus-kasus pengujian}
%			\label{testcase-i}                                                           
%			\\ \hline
%			\centering\bfseries{ID} & \centering\bfseries{Service (Fungsi)} & \centering\bfseries{Extra Latency} & \centering\bfseries{User} & \centering\bfseries{Keterangan} \tabularnewline \hline
%			\endfirsthead
%			I1 & CheckoutService (placeorder) &  \centering{100ms} & \centering{25} & Kasus extra latency \#1 \\ \hline
%				
%		\end{longtable}
\begin{table}[]
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\multicolumn{1}{|c|}{ID} & \multicolumn{1}{c|}{Service (Fungsi)} & Extra Latency & User & Keterangan              \\ \hline
		I1                       & CheckoutService (placeorder)          & 100ms         & 25   & Kasus extra latency \#1 \\ \hline
	\end{tabular}
\end{table}
